PANNEURO_analysis

### 2020-10-26 PANNEURO_analysis_WHO_pres.Rmd
rowsums_who

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/baseline_and_cfs_wave6.rds")) #NEEDS CHANGING
dim(dat.raw)
colnames(dat.raw)
```

@@

>>>>

## Read in data
```{r read in data}
dat.raw <- readRDS(file = paste0(data_path, "/four_cohorts.rds")) #NEEDS CHANGING
dim(dat.raw)
colnames(dat.raw)
```

@@

# ALSfrs
```{ALSfrs col names r}
als.col.names <- dat.raw %>%
  select(
    starts_with("alsfrs") & ends_with("numeric")
  ) %>%
  colnames()

```

```{ALSfrs row sums r}
dat.raw <- dat.raw %>%
  mutate(als.sum.score =
  rowSums(select(.,als.col.names), na.rm = F)
   )
```

```{ALSfrs frequencies r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(als.sum.score)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, als.sum.score) %>%
  mutate(Prop = round(n/sum(n), 2))

```
# ESS
```{ESS col names r}
ess.col.names <- dat.raw %>%
  select(
    starts_with("ess") & ends_with("numeric")
  ) %>%
  colnames()

```

```{ESS row sums r}
dat.raw <- dat.raw %>%
  mutate(ess.col.names =
   rowSums(select(.,als.col.names), na.rm = F)
   )
```

```{ESS frequencies r}
dat.raw %>%
  filter(!is.na(startDate.coping)) %>%
  filter(!is.na(covid_probable_case_incl_screening)) %>%
  filter(!is.na(ess.col.names)) %>%
  group_by(covid_probable_case_incl_screening) %>%
  count(covid_probable_case_incl_screening, ess.col.names) %>%
  mutate(Prop = round(n/sum(n), 2))
```
